Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/results.tex
edit intro text on Results section

%!TEX root = ClementiBarba2020.tex

\subsection{Replication of results from Rockstuhl, et al., 2005}

@@

 \subsection{Replication of results from Ellis et al., 2016, and validation}

>>>>

%!TEX root = ClementiBarba2020.tex
All the results reported in this paper were obtained using the \pygbe software \cite{ClementiETal2017},
with the version at commit \href{https://github.com/pygbe/pygbe/tree/e1f3650b0c99cab99dcfe5372200d3a1534eddfe}{34eddfe} in the history.
The software GitHub repository contains a Dockerfile to create the container image where we ran the simulations. 
The manuscript GitHub repository is separate from the software repository, and can be found at \url{https://github.com/barbagroup/pygbe_validation_paper}.
It contains the reproducibility packages for all results, as described in sub-section \ref{sec:reprod} and elsewhere in the paper.
We used a lab workstation for all simulations, built from parts.
Hardware specifications are as follows: 
\begin{compactitem}
  \item[$\triangleright$] CPU: Intel Core i7-5930K Haswell-E 6-Core 3.5GHz LGA 2011-v3
  \item[$\triangleright$] RAM: G.SKILL Ripjaws 4 series 32GB (4 x 8GB)
  \item[$\triangleright$] GPU: Nvidia Tesla K40c (with 12 GB memory)
\end{compactitem}

\paragraph{Solver parameters:} We used a GMRES exit tolerance of $1\times10^{-6}$ in the iterative solver for all our simulations. Details on the treecode and integration parameters (and others)
can be found within input files included in the manuscript GitHub repository as part of the reproducibility packages (``repro-packs'').

\paragraph{Run times:} We report detailed time logs together with the data of our simulations, as part of the repro-packs to accompany this paper. Here is a brief report.
For the result of the replication of Figure 14 of Rockstuhl et al., sub-section \ref{sec:replication1}, the total wall-clock time for producing each curve was approximately 11.6 hours, which is the result of computing
the extinction cross section for 175 wavelength cases, giving $\approx$4 minutes per run. In the case of the validation and replication of Figure 2a of Ellis et al., sub-section \ref{sec:replication2}, 
the total wall-clock time for producing the curve was approximately 2.3 hours, which is the result of computing
the extinction cross section for 208 wavelength cases, giving $\approx$40 seconds per run.

\subsection{Replication of results from Rockstuhl, et al., 2005}\label{sec:replication1}

@@

 \subsection{Replication of results from Ellis et al., 2016, and validation}\label{sec:replication2}
